
\documentclass[a4paper,12pt]{article}

\usepackage{fancyhdr}
\usepackage{amssymb}
%\usepackage{mathpazo}
\usepackage{mathtools}
\usepackage{amsmath}
\usepackage{slashed}
\usepackage{cancel}
\usepackage[mathscr]{euscript}
\usepackage{MaxPackage} %Note: You need MaxPackage installed or in the same folder as your .tex file or something.

\newcommand{\colorcomment}[2]{\textcolor{#1}{#2}} %First of these leaves in comments. Second one kills them.
%\newcommand{\colorcomment}[2]{}


\pagestyle{fancy}
\lhead{Linear Algebra}
\chead{MA265}
\rhead{Quiz 10, 7/28/2015}

%Number of Problems		: 
%Clear					:
%Begun					:
%Not started			:
%Can complete via book	:
%Needs Polish			:

%Pomodoros logged		:

\begin{document}

{\Large{\bf Problem 1:}} Let \[ A= \left( \begin{array}{ccc}0 & 1 \\ -1 & 0\end{array} \right)\]

a) Find $A$'s characteristic polynomial, real eigenvalues, and bases for their associated eigenspaces.

$\la^2 +1 =0$, no real eigenvalues.

b) What is the row-reduced echelon form of $A$? For rref($A$), find the characteristic polynomial, real eigenvalues, and bases for their associated eigenspaces?

$(\la -1)^2$, eigenvalue is $1$, any basis for $\R^2$ works. 
\shunt

{\Large{\bf Problem 2:}}Define:

a) Inner Product:

I had originally wanted:

``An inner product on $V$ is a function (written $(\cdot, \cdot)$) from $V^2$ to $\R$ such that for all $u,v,w \in V$, $c \in \R$:

1) $(u,u) \geq 0$, $(u,u)=0$ if and only if $u = 0_V$

2) $(v,u) = (u,v)$

3) $(u+v,w) = (u,w) + (v,w)$

4) $(cu,v) = c(u,v)$''

I also took the definition of ``dot product'' in $\R^n$ (think: $\sum a_mb_m$), as only one person got close to the correct answer.

b) Orthonormal: A set of vectors, $S$, in $V$ is orthonormal if each pair of vectors is orthogonal and $\norm{u} = 1$ for all $u \in S$.

c) Eigenvalue: We say that $\la$ is an eigenvalue of a matrix (or linear transformation) if $Ax=\la x$ (or $T(x) = \la x$ for some vector $x$.

d) Eigenvector: The eigenvectors associated with an eigenvalue, $la$, are the vectors $x$ satisfying $Ax=\la x$ (or $T(x) = \la x$).

Anything close to ``the definition in the book'' gets points. I tend to give a lot of leeway assigning points for these problems.

\shunt

{\Large{\bf Problem 3:}} Must a matrix with real entries have any real eigenvalues? 

No. See problem 1 for a counterexample.

Points aren't given without an explanation of some sort.

\end{document}